N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex
Fix a typo and adding one more sentence

  \subsection{Creating an Abstract Game Engine}
  % How we came up with the abstract design
  The design for our game engine stemmed from trying to isolate the common
  general components of what would be required to create a running game.
  Rather than focus on creating one specific game implementation - we wanted to
  look at the larger picture and view the problem in terms of the common pattern
  that emerged between these kinds of games.

  Each of the portions of the \textit{State}-\textit{Actions}-\textit{Agents}
  design is independent so that - once created - it does not rely on other
  modules for it's internal pieces.
  Each of the constituent parts of the game engine is more akin to a node on a
  graph and the interfaces are like edges.
  The pieces should be thought of as islands of code that could then interact
  with other modules. By using the game model to define a specific game - we
  essentially create more specific versions of those islands following the
  recipe spelled out in the signatures.

>>>>

  \subsection{Creating an Abstract Game Engine}
  % How we came up with the abstract design
  The design for our game engine stemmed from trying to isolate the common
  general components of what would be required to create a running game.
  Rather than focus on creating one specific game implementation where these
  problems are addressed in an \textit{ad hoc} way - we wanted to
  look at the larger picture and view the problem in terms of the common pattern
  that emerged between these kinds of games.

  Each of the portions of the \textit{State}-\textit{Actions}-\textit{Agents}
  design is independent so that - once created - it does not rely on other
  modules for its internal pieces.
  Each of the constituent parts of the game engine is more akin to a node on a
  graph and the interfaces are like edges.
  The pieces should be thought of as islands of code that could then interact
  with other modules. By using the game model to define a specific game - we
  essentially create more specific versions of those islands following the
  recipe spelled out in the signatures.
